A word-sense representation for documents based on information value and word sense disambiguation

### 2014-03-21 paper/refactor.tex
Remove some comments.|

\begin{itemize}
  \item Mention the crawler for the complete lenin works, pointing that finally we didn't used it but that the scrapper is available in the project at github
  \item May be, point out some numbers of the db generated. (total documents, mean tokens per document, etc). It's my opinion, I understand that it's not the main line of the project.
\end{itemize}

>>>>

For this purpose, we developed a web crawler to fetch the works from the \cite{LENIN}, but ended up using only these works.
